

{1) After completing the lab, answer again the question posed in the pre- lab: If the glider/cart and the hanger had equal masses, will the magnitude of the acceleration of the glider/cart be $g$, less than $g$, or bigger than $g$ ? Explain why in words. If, after doing the lab, your answer changed, explain what you had wrong when you first made your prediction.}

{If the cart and the hanger had equal masses, the acceleration would have been 4.9 $m/s^2$.}

	$$a_{c} = \frac{m_{h}g}{m_{h} + m_{c}}$$
	
	$$a_{c} = \frac{mg}{2m} = \frac{g}{2} \approx 4.9 m/s^2$$

{2) In the special case where $m_{h}$ is much larger than $m_{g}$, what do you expect the acceleration of the system to be? Does your formula agree with this special case ?}

{When $m_{h}$ is much larger than $m_{g}$, the acceleration is significantly less because acceleration is inversely proportional to the mass.}

{3) In the special case where $m_{h}$ is much smaller than $m_{g}$, what do you expect the acceleration of the system to be ? Does your formula agree with this special case ?}

{When $m_{h}$ is much smaller than $m_{g}$, the acceleration is significantly higher because acceleration is inversely proportional to the mass.}

{4) Throughout this lab, we neglected friction. If friction were present (it always is, to some degree), how would your results be affected ? Would the slope of your measured line be larger or smaller than the predicted slope ?}

{According to Newton's second law, an object's acceleration is inversely correlated with its net external force. Friction always acts in the direction opposing motion. As a result, the measured line's slope should be lower than the expected slope.}

{5) Conceptually, what differences would you expect to see between the two apparatus (Air Track & Glider vs. Rail & Cart) ? Comment on the need for different weights between the two systems. While in the lab: discuss your results with the group sitting across from you, are there any noticeable differences ? Try to provide some explanation for these differences.}

{Conceptually, the differences between the two apparatuses are compensating for the differences in weights because the cart is expected to be far heavier than the air glider.}


